---
title: "GDPArea"
author: "Phil Hall"
date: "26 May 2018"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

source("processData.R")
library(ggplot2)
library(plotly)

```

```{r latest, include=FALSE}

lastQ <- data[data$Date == max(data$Date),]

```

Latest Quarterly change

`r lastQ$Date`

`r if (lastQ$GDPAreaQ < 0) {"DOWN"} else {"UP"}` `r round(sqrt(lastQ$GDPAreaQ^2), digits = 1)`%

```{R quarterbars, include=FALSE}

shortTrend$val <- "neg"
shortTrend$val[shortTrend$GDPAreaQ >= 0] <- "pos"

Qbars <- plot_ly() %>% 
  add_bars(data = shortTrend, x = ~as.character(Date), y = ~GDPAreaQ, 
           color = ~val, colors = c("red","blue"), 
         hoverinfo = 'text', 
           text = ~paste0(as.character(Date),
                          '<br>',
                          round(GDPAreaQ,2))) %>%
  layout(showlegend = FALSE,
         xaxis = list(title = ""),
         yaxis = list(title = "% change since last quarter"))

```

`r Qbars`

```{R yearline, include=FALSE}

Yline <- plot_ly(data = shortTrend, x = ~as.character(Date), y = ~GDPAreaY, type = 'scatter', mode = 'lines',
                  hoverinfo = 'text', 
                  text = ~paste0(as.character(Date),
                          '<br>',
                          round(GDPAreaY,2))) %>%
                  layout(showlegend = FALSE,
                    xaxis = list(title = ""),
                    yaxis = list(title = "% change since last year")) 
         

```

`r Yline`



